---
title: "R Notebook"
output: html_notebook
author: "Joseph Pope"
date: "2/11/2020"
---

[Hotels!](https://github.com/rfordatascience/tidytuesday/tree/master/data/2020/2020-02-11)


```{r init, include=FALSE}
library(tidyverse)
library(lubridate)

hotels <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2020/2020-02-11/hotels.csv')

```

```{r tidyverts}

library(fable)
library(feasts)
library(tsibble)

hotels2 <- hotels %>%
  mutate(arrival_date = ymd(str_c(arrival_date_year, arrival_date_month, arrival_date_day_of_month)))

hotels2 %>%
  as_tsibble(index = reservation_status_date, key = arrival_date) %>%
  gg_season(adult)

```






Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.
